%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV for A4 paper format
% XeLaTeX Template
% Version 1.1
%
% A4 version author:
% Marvin Frommhold (depressiverobot.com)
% https://github.com/depressiveRobot/friggeri-cv-a4
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Options
% 'print': remove colors from this template for printing
% 'nocolors' to disable colors in section headers

\documentclass[]{friggeri-cv-a4}

\usepackage{enumitem}

\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}
\setlist{noitemsep}

\header{Stephen}{Price}{Researcher, Statistician \& Data Scientist} % Your name and current job title/field

%----------------------------------------------------------------------------------------
% SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{Contact}
%Dudley, UK
%+44 7800 896114
\href{mailto:sjamesprice@gmail.com}{\small{sjamesprice@gmail.com}}
~
\section{Links}
\href{https://2infectious.wordpress.com}{Research site}
\href{https://scholar.google.co.uk/citations?user=Ob0mGTUAAAAJ&hl=en&oi=sra}{Google scholar}
\href{https://www.researchgate.net/profile/Stephen_Price10}{ResearchGate}
\href{https://github.com/lizardburns}{GitHub}
~
~
~
\section{Programming}
R
bash
Python
SQL
~
\section{Modelling}
Regression (LM, GLM)
additive (GAM)
mixed-effects
machine learning
spatial
~
~
%\section{Reporting}
%markdown
%Word
%LaTeX
~
\section{Awards}
UoN Zoology prize
QMUL volunteer of the year
Ofqual recognition awards for innovation and impact
~
~
~
\section{References}
Ofqual, on request
\href{mailto:Trent.Garner@ioz.ac.uk}{Trent Garner, ZSL}
~
\end{aside}

%----------------------------------------------------------------------------------------
%	PROFILE SECTION
%----------------------------------------------------------------------------------------

%\section{profile}
%\hspace{0.75cm} Highly analytical, extremely versatile and educated to PhD level, I am a strong independent learner with a determined attitude and experience of leading projects to success. Resilient and accustomed to overcoming challenges through problem-solving and collaboration, I bring a track record of working innovatively to tease out meaning from complex datasets and deliver findings to stakeholders through professional reports and clear presentations.

%\hspace{0.75cm} As an \textbf{investigator}, I use my creativity and logic to design experiments and plan workflows which generate data using cutting-edge technologies. As an \textbf{analyst}, I use sophisticated methods to analyse a variety of datasets with bespoke scripts and pipelines tailored to individual problems. As a \textbf{project manager}, I have experience of funding applications, budgets, staff supervision and development, and building networks.

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}

%------------------------------------------------

\entry
{2019--2021}
{Senior Research \& Data Analyst}
{Ofqual}
{%
%\begin{itemize}
%\setlength\itemsep{-1em}
\textbf{Innovation:} supported projects across Research, Data \& Analytics and Standards teams by bringing innovations and delivering bespoke solutions, e.g. development of a QR code based mark-tracking system. \\
\textbf{Reproducible analytical pipelines:} developed a suite of internal R packages for cleaning, quality-checking, and analysis of Official Statistics and exam grading datasets, including functions \& unit tests, documentation \& vignettes. \\
\textbf{Data engineering:} wrote R pipelines to join raw datasets and engineer features to support regulation of standards in assessment. \\
\textbf{Interactive applications:} routinely produced interactive R Shiny apps: 4 published apps, 20 internal, 1 private external. Transformed analysis of consultations through use of bespoke internal apps enabling more than 30 users to make informed decisions under pressure. \\
\textbf{Data visualisation:} wrote R package to implement company brand and style in data visualisations. Includes vignettes packed with examples \& best practise.%
%\end{itemize}%
}

%------------------------------------------------

\entry
{2013--2019}
{Research Scientist}
{UCL \& ZSL Institute of Zoology}
{Investigated the spread and evolution of viruses using genomics, laboratory experiments and field studies. Collaborated with 19 research groups in 16 countries. \\
\textbf{Problem-solving:} iterative experimental design, logistics/planning of field-based projects. \\
\textbf{Data analysis:} from genomics to GIS and citizen science datasets. Routinely used statistical models (LM, GLM, GAM, mixed-effects). Also used machine learning approaches. As a supervisor, collaborator \& peer reviewer, I reviewed data summaries and identified patterns in raw data requiring further investigation. \\
\textbf{Method Development:} molecular and cell culture systems to study viruses. \\
\textbf{Leadership:} contributed to or led projects that won £800,000 in funding. Supervised 7 postgraduate and 7 undergraduate students as well as technical staff. \\
\textbf{Publication:} \href{https://2infectious.wordpress.com/publications}{27 articles in academic journals} since 2013 \& 2 magazine articles.}

%------------------------------------------------

\entry
{2010--2012}
{Biodiversity Programme Schools Coordinator}
{Conserve Me Foundation}
{Part of a team that created \& delivered a 6-week programme of workshops on biodiversity and the environment. Received the QMUL volunteer of the year award.}

%------------------------------------------------

\entry
{2009}
{Parasitology Research Technician}
{University of Bristol}
{Planned and conducted lab experiments \& reported results to senior scientists.}

%------------------------------------------------

\entry
{2008--2009}
{Project Manager}
{wibfilm}
{Prepared pitches and proposals, coordinated teams/kit, administered finances.}

%------------------------------------------------

\entry
{2003--2004}
{Assistant Quality Manager}
{LB Parkes Ltd}
{Monitored chemical concentrations and safety records for industrial processes.}

%------------------------------------------------

\entry
{1998--1999}
{English Teacher}
{Pamir Public School, Pakistan}
{Created and delivered a curriculum for 5-16 year olds in a school in an isolated, subsistence-farming community in the Hindu Kush.}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}

%------------------------------------------------

\entry
{2009--2013}
{PhD {\normalfont Epidemiology/Conservation/Population Genetics}}
{Queen Mary University of London}
{\emph{Emergence of a virulent wildlife disease: using spatial epidemiology and phylogenetic methods to reconstruct the spread of amphibian viruses}}

%------------------------------------------------

\entry
{2004--2007}
{BSc Hons Zoology}
{University of Nottingham}
{1\textsuperscript{st} class honours; awarded Zoology prize for top mark in year}

%------------------------------------------------

\end{entrylist}

\newpage
\newgeometry{left=2.54cm, top=2.54cm, bottom=2.54cm}

%----------------------------------------------------------------------------------------
% training section
%----------------------------------------------------------------------------------------

\section{training (selected courses)}

\textbf{ONS Secure Research Service Accredited Researcher training (2019)};
\textbf{Advanced Python} PR Statistics (2018);
\textbf{Managing Big Data with MySQL} MOOC from Duke University (2018);
\textbf{Programming for Everybody (Python)} MOOC from University of Michigan (2015);
\textbf{Grant Writing \& Project Management} British Ecological Society (2013);
\textbf{R Statistical Programming} Institute of Zoology (2011);
\textbf{ArcGIS} Institute of Zoology (2010)

%----------------------------------------------------------------------------------------
%	PRESENTATION SECTION
%----------------------------------------------------------------------------------------

\section{presentations \& media coverage}

\begin{itemize}
\item 12 talks at international conferences
\item seminars \& presentations to academics, stakeholders \& the public
\item regular presentations at group and departmental meetings
\item conceived and supervised production of \href{https://2infectious.wordpress.com/2019/06/25/where-did-the-frogs-go-and-why/}{an animated movie narrated by Stephen Fry} for dissemination of research findings to diverse audience
\item I promoted my work through \href{https://2infectious.wordpress.com/in-the-media/}{specialist and mainstream media}, including the New Scientist, BBC radio and national daily newspapers. An overview of my online reach is available via \href{https://profiles.impactstory.org/u/0000-0001-6983-6250}{Impact Story}.
\end{itemize}

%----------------------------------------------------------------------------------------
% PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\section{publications}

\printbibsection{article}{Selected journal articles} % Print all articles from the bibliography
\printbibsection{report}{Reports} % Print all articles from the bibliography

%----------------------------------------------------------------------------------------

\end{document}
